### 2014-10-16 Neutral_simulPow.Rmd
Change powerNeutral_1T_D1 for compute power D_1SRS & D_0SAD add more methods

## Simulations with different parameters using pomac and at Time=100

@@

## Calculate power of SAD DqSAD DqSRS for parameters

@@

pow_AD <- data.frame()
comp_AD<- data.frame()
cc <- foreach(i=1:nrow(simul)) %dopar%
{
    powerNeutral_1Time(simul[i,],0.2, 0.04, 0.001) # Mortality,Dispersal,Colonization
}

for(i in 1:nrow(simul)) {
pow_AD <- rbind(pow_AD, cc[[i]]$pow_AD)
comp_AD<- rbind(comp_AD,cc[[i]]$comp_AD)
}
rm(cc)
pow_AD$MrtR <- 0.2
pow_AD$DspD <- 0.04
pow_AD$ClnR <- 0.001

@@

#pow_AD <- rbind(pow_AD,cc$pow_AD)
#comp_AD<- rbind(comp_AD,cc$comp_AD)
#rm(cc)

@@

for(i in 1:nrow(simul)) {
	p_AD <- rbind(p_AD, cc[[i]]$pow_AD)
	comp_AD<- rbind(comp_AD,cc[[i]]$comp_AD)
}
rm(cc)
p_AD$MrtR <- mm
p_AD$DspD <- dd
p_AD$ClnR <- co

pow_AD <- rbind(pow_AD, p_AD)

@@

for(i in 1:nrow(simul)) {
    p_AD <- rbind(p_AD, cc[[i]]$pow_AD)
	comp_AD<- rbind(comp_AD,cc[[i]]$comp_AD)
}
rm(cc)
p_AD$MrtR <- mm
p_AD$DspD <- dd
p_AD$ClnR <- co

pow_AD <- rbind(pow_AD, p_AD)

stopCluster(cl)
rm(p_AD)
setwd(oldcd)
save.image()
```
# Make plots of power!

@@

require(ggplot2)
pow_AD$MeanSp <- as.numeric(pow_AD$MeanSp)
pow_AD$power <- as.numeric(pow_AD$power)
pow_AD$typeI <- as.numeric(pow_AD$typeI)

# Add field with combination of dispersal & mortality 
pow_AD$DspMrt <- with(pow_AD,paste0(DspD," - ",MrtR))

# Add number of species in the metacommunity
pow_AD$spMeta <- ceiling(as.numeric(pow_AD$NumSp)*1.33)

g <- ggplot(pow_AD,aes(x=spMeta,y=power)) + geom_point(shape=19,aes(size=typeI,colour=DspMrt)) + facet_grid(Side ~ Type) +
  ylab(bquote("Rejection Rate of"~H[0]~"(" ~alpha~"= 0.05)")) +
  xlab("Metacommunity species number") +
  scale_size_continuous(name="Type I error") +
  scale_colour_discrete(name="Disp - Mort")

@@

g <- ggplot(pow_AD,aes(x=MeanSp,y=typeI)) + geom_point(shape=19,aes(size=power,colour=DspMrt)) + facet_grid(Side ~ Type)
g+theme_bw()

comp_AD$spMeta <- ceiling(as.numeric(comp_AD$NumSp)*1.33)

# Calculate power in fuction of replacement rate difference
# Falta cambiar NumSp por 
c1 <- with(comp_AD,comp_AD[MrtR1==MrtR2 & DspD1==DspD2 & ClnR1==ClnR2 & RplR2!=RplR1,])
c1$DifR <- with(c1,abs(RplR2-RplR1))
c2 <- ddply(c1,.(NumSp,Type,DifR),hh)

@@

# Calculate TypeI error in fuction of replacement rate
c1 <- with(comp_AD,comp_AD[MrtR1==MrtR2 & DspD1==DspD2 & ClnR1==ClnR2 & RplR2==RplR1,])
c3 <- ddply(c1,.(NumSp,Type,RplR2),hh)
names(c3)[4]<-"typeI"
g <- ggplot(c3,aes(x=RplR2,y=typeI)) + geom_point(shape=19,aes(colour=as.factor(Type))) + facet_grid( NumSp ~ .)
g+theme_bw()

@@

```{r testAD_factors, eval=F,echo=F,message=T,warning=T}
require(plyr)
hh <-function(x) {
  t <- nrow(x)
  s <- nrow(x[x$p.value<0.05,])
  data.frame(count=s,power=s/t,n=t)
}
# Calculate power
c1 <- with(comp_AD,comp_AD[MrtR1==MrtR2 & DspD1==DspD2 & ClnR1==ClnR2 & RplR2!=RplR1,])
c1$DifR <- with(c1,abs(RplR2-RplR1))
c2 <- ddply(c1,.(NumSp,Side,Type,MrtR1,DspD1,DifR),hh)
#require(dplyr)
#c2 <- tbl_df(c1)
#c3 <- c2 %>% 
#  group_by(NumSp,Side,Type,MrtR1,DspD1,DifR) %>% 
#  filter(p.value<0.05) %>% 
#  summarize(tot=n()) %>% 
#  summarize(pgt5=n()) 
model1 <-glm(count~NumSp*Side*Type*MrtR1*DspD1*DifR,poisson,data=c2)
summary(model1)
plot(model1)

@@

# Use the information dimension t-test with sd from

@@

cc <- foreach(i=1:nrow(simul)) %dopar%
{
    powerNeutral_1T_D1(simul[i,],log2(simul$side)-1,1,0,0,0.001)
}
pow_TD1 <- data.frame()
comp_TD1<- data.frame()

@@

The power of D1 is around .5 too low

Lets check

@@

simul <- foreach(i=1:nrow(ps),.combine='rbind') %dopar%
{
    print(ps[i,])
    simulNeutral_1Time(ps$nsp[i],ps$si[i],500,"L",20,F)
}
stopCluster(cl)

@@

```{r power_GCq10test, eval=F,echo=F,message=T,warning=T}
setwd("Simul")

@@

cc <- foreach(i=1:nrow(simul)) %dopar%
{
    powerNeutral_1T_GC(simul[i,],3,0,0,0.001,10)
}
pow_GCq10 <- data.frame()
comp_GCq10<- data.frame()

>>>>

## Neutral Simulations

@@

## Calculate power of SAD DqSAD DqSRS using q=[-24,24]

@@

pow_ADq24 <- data.frame()
comp_ADq24<- data.frame()
cc <- foreach(i=1:nrow(simul)) %dopar%
{
    powerNeutral_1Time(simul[i,],0.2, 0.04, 0.001) # Mortality,Dispersal,Colonization
}

for(i in 1:nrow(simul)) {
pow_ADq24 <- rbind(pow_ADq24, cc[[i]]$pow_AD)
comp_ADq24<- rbind(comp_ADq24,cc[[i]]$comp_AD)
}
rm(cc)
pow_ADq24$MrtR <- 0.2
pow_ADq24$DspD <- 0.04
pow_ADq24$ClnR <- 0.001

@@

@@

for(i in 1:nrow(simul)) {
	p_AD <- rbind(p_AD, cc[[i]]$pow_AD)
	comp_ADq24<- rbind(comp_ADq24,cc[[i]]$comp_AD)
}
rm(cc)
p_AD$MrtR <- mm
p_AD$DspD <- dd
p_AD$ClnR <- co

pow_ADq24 <- rbind(pow_ADq24, p_AD)

@@

for(i in 1:nrow(simul)) {
    p_AD <- rbind(p_AD, cc[[i]]$pow_AD)
	comp_ADq24<- rbind(comp_ADq24,cc[[i]]$comp_AD)
}
rm(cc)
p_AD$MrtR <- mm
p_AD$DspD <- dd
p_AD$ClnR <- co

pow_ADq24 <- rbind(pow_ADq24, p_AD)

stopCluster(cl)
rm(p_AD)
setwd(oldcd)
save.image()
```
# Make plots of power! using q=[-24,24]

@@

require(ggplot2)
pow_ADq24$MeanSp <- as.numeric(pow_ADq24$MeanSp)
pow_ADq24$power <- as.numeric(pow_ADq24$power)
pow_ADq24$typeI <- as.numeric(pow_ADq24$typeI)

# Add field with combination of dispersal & mortality 
pow_ADq24$DspMrt <- with(pow_ADq24,paste0(DspD," - ",MrtR))

# Add number of species in the metacommunity
pow_ADq24$spMeta <- ceiling(as.numeric(pow_ADq24$NumSp)*1.33)

g <- ggplot(pow_ADq24,aes(x=spMeta,y=power)) + geom_point(shape=19,aes(size=typeI,colour=DspMrt)) + facet_grid(Side ~ Type) +
  ylab(bquote("Rejection Rate of"~H[0]~"(" ~alpha~"= 0.05)")) +
  xlab("Metacommunity species number") +
  scale_size_continuous(name="Type I error") +
  scale_colour_discrete(name="Disp - Mort")

@@

g <- ggplot(pow_ADq24,aes(x=MeanSp,y=typeI)) + geom_point(shape=19,aes(size=power,colour=DspMrt)) + facet_grid(Side ~ Type)
g+theme_bw()

# Recalculate power from comp_ADq24
#
require(plyr)
hh <-function(x) {
  t <- nrow(x)
  s <- nrow(x[x$p.value<0.05,])
  data.frame(power=s/t,n=t)
}

comp_ADq24$spMeta <- ceiling(as.numeric(comp_ADq24$NumSp)*1.33)

# Calculate power in fuction of replacement rate difference
# Falta cambiar NumSp por 
c1 <- with(comp_ADq24,comp_ADq24[MrtR1==MrtR2 & DspD1==DspD2 & ClnR1==ClnR2 & RplR2!=RplR1,])
c1$DifR <- with(c1,abs(RplR2-RplR1))
c2 <- ddply(c1,.(NumSp,Type,DifR),hh)

@@

# Calculate TypeI error in fuction of replacement rate
c1 <- with(comp_ADq24,comp_ADq24[MrtR1==MrtR2 & DspD1==DspD2 & ClnR1==ClnR2 & RplR2==RplR1,])
c3 <- ddply(c1,.(NumSp,Type,RplR2),hh)
names(c3)[4]<-"typeI"
g <- ggplot(c3,aes(x=RplR2,y=typeI)) + geom_point(shape=19,aes(colour=as.factor(Type))) + facet_grid( NumSp ~ .)
g+theme_bw()

@@

```{r testAD_factors, eval=F,echo=F,message=T,warning=T}
require(plyr)
hh <-function(x) {
  t <- nrow(x)
  s <- nrow(x[x$p.value<0.05,])
  data.frame(count=s,power=s/t,n=t)
}
# Calculate power
c1 <- with(comp_ADq24,comp_ADq24[MrtR1==MrtR2 & DspD1==DspD2 & ClnR1==ClnR2 & RplR2!=RplR1,])
c1$DifR <- with(c1,abs(RplR2-RplR1))
c2 <- ddply(c1,.(NumSp,Side,Type,MrtR1,DspD1,DifR),hh)
#require(dplyr)
#c2 <- tbl_df(c1)
#c3 <- c2 %>% 
#  group_by(NumSp,Side,Type,MrtR1,DspD1,DifR) %>% 
#  filter(p.value<0.05) %>% 
#  summarize(tot=n()) %>% 
#  summarize(pgt5=n()) 
model1 <-glm(count~NumSp*Side*Type*MrtR1*DspD1*DifR,poisson,data=c2)
summary(model1)
plot(model1)

@@

# Use the information dimension t-test

@@

cc <- foreach(i=1:nrow(simul)) %dopar%
{
    powerNeutral_1T_D1(simul[i,],log2(simul$side)-1,1,0.2,0.04,0.001)
}
pow_TD1 <- data.frame()
comp_TD1<- data.frame()

@@

## Plot power of D1

@@

simul <- foreach(i=1:nrow(ps),.combine='rbind') %dopar%
{
    simulNeutral_1Time(ps$nsp[i],ps$si[i],500,"L",20,F)
}
stopCluster(cl)

@@

```{r power_GCq10test, eval=T,echo=F,message=T,warning=T}
setwd("Simul")

@@

cc <- foreach(i=1:nrow(simul)) %dopar%
{
    powerNeutral_1T_GC(simul[i,],3,40.2,0.0,0.001,10)
}
pow_GCq10 <- data.frame()
comp_GCq10<- data.frame()
